### 2018-09-05 paper/preliminaries.tex
Proofs for Lemma 1 completed

In this section, we present CSP and the concept of minimal hitting set, which
is central to our novel notion of test for failures refinement.

% =========================================================================
\subsection{CSP and Refinement}

%First, we introduce the CSP notation and refinement notions. We then discuss
%a graph-based semantics for finite-state CSP processes.

% =========================================================================
%\subsubsection*{CSP}
%\label{section:CSP}

@@

@@

Two forms of choice support branching behaviour. An external choice $P
\extchoice Q$ between processes $P$ and $Q$ offers to the environment the
initial events of $P$ and $Q$. Once synchronisation takes place, the process
that has offered this event is chosen and the other is discarded. In an
internal choice $P \intchoice Q$, the environment does not have an
opportunity to interfere:~the choice is made by the process.
%
\begin{example}\label{example:CSP}
  We consider $P$, $Q$, and $R$ below. $P$ is initially
  ready to engage in the event $a$, and then makes an internal  choice to
  behave like either $Q$ or $R$.
  \begin{eqnarray*}
  P & = & a \then (Q\intchoice R)
  \\
  Q & = & a \then P \extchoice c \then P
  \\
  R & = & b \then P \extchoice c \then R
  \end{eqnarray*}
  $Q$, for instance, offers to the environment the choice to engage in $a$
  again or $c$. In both cases, afterwards, we have a recursion back to $P$.
  In $R$, if $b$ is chosen, we also have a recursion back to $P$. If $c$ is
  chosen, the recursion is to $R$.
  \xbox
\end{example}
%
Iterated forms $\Extchoice i: I @ P(i)$ and $\Intchoice i: I @ P(i)$ of the
external and internal choice operators allow us to define a choice over a
collection of processes $P(i)$. By convention, , if the index set $I$ is
empty, external choices evaluate to the process $\Stop$, which
deadlocks:~does not engage into any event and does not terminate. An iterated
internal choice is not defined for an empty index set.

@@

Failures refinement, $P \lessdet_F Q$, is defined as expected by set
containment $\fails(Q)\subseteq\fails(P)$. Since refusals are subset-closed,
$(s,\varnothing)\in\fails(P)$ for all traces $s\in\trc(Q)$. So, for
divergences-free processes, failures refinement implies trace refinement.
Therefore, using the conformance relation
%
\begin{equation}\label{eq:conf}
  Q\ conf\ P \defs \forall s\in \trc(P) \cap \trc(Q): \refs(Q/s)
  \subseteq \refs(P/s),
\end{equation}
%
failures refinement can be expressed by $\lessdet_T$ and $conf$.
%
\begin{equation}\label{thm:fref-tref-conf}
(P \lessdet_F Q) \iff (P \lessdet_T Q \land Q\ conf\ P)
\end{equation}
%
Throughout this paper, the alphabet of the processes, that is the set of
events that are in scope, is denoted by $\Sigma$ and supposed to be finite.
%Since we are only
%considering ``classical'' CSP processes, the alphabet is always finite.
The FDR tool~\cite{fdr} supports model checking and semantic analyses of
finite-state CSP processes.

For finite CSP processes, since refusals are
subset-closed, $\refs(P/s)$ can be constructed from the set of \emph{maximal
refusals} defined by
%
\begin{equation}
\maxrefs(P/s) = \{ R \in\refs(P/s)~|~\forall R'\in \refs(P/s) - \{ R\}: R \not\subseteq R'\}
\end{equation}
%
Conversely, with the maximal refusals $\maxrefs(P/s)$ at hand, we can
reconstruct the refusals in the set $\refs(P/s)$ as described by
%
\begin{equation}
\refs(P/s) = \{ R'\in\power(\Sigma)~|~\exists R\in \maxrefs(P/s): R'\subseteq R \}.
\end{equation}
%
Deterministic process states $P/s$ have exactly the one maximal refusal
defined by $\Sigma-[P/s]^0$, where $[P/s]^0$ denotes the \emph{initials} of
$P/s$, that is, the events that $P/s$ may engage into. The maximal refusals
in combination with the initials of a process express its degree of
nondeterminism.
%
\begin{example}
\label{ex:nondetdegree} $P = (\Stop \intchoice Q)$ has maximal refusals
$\maxrefs(P) = \{ \Sigma \}$, because $\Stop$ refuses to engage in any event,
and this is carried over to $P$ by the internal choice. However, $P$ is
distinguished from $\Stop$ by its initials, which are defined by $[P]^0 = [
\Stop \intchoice Q]^0 = [Q]^0$. So $P$ may engage nondeterministically in any
initial event of $Q$, but also refuse everything, due to internal selection
of $\Stop$.

Assuming an alphabet $\Sigma = \{a,b,c,d\}$, the process
%
$$Q = (e:\{a,b\} \then \Stop) \intchoice (e:\{c,d\} \then \Stop)$$
%
has maximal refusals $\maxrefs(Q) = \{ \{c,d\}, \{a,b\} \}$ and initials
$[Q]^0=\Sigma$. In contrast to $P$, nondeterminism is reflected by
two maximal refusals. \xbox
\end{example}

@@

The total function $r$ maps each node $n$ to a non-empty set of  (possibly
empty) subsets of $\Sigma$. The graph construction guarantees that
$r(G(P)/s)$ represents the maximal refusals of $P/s$ for all $s\in\trc(P)$.
As a consequence,
\begin{equation}\label{eq:refsAndR}
(s,X)\in\fails(P) \iff s\in\trc(G(P)) \wedge \exists R\in r(G(P)/s): X\subseteq R,
\end{equation}
so $G(P)$ allows us to re-construct the failures semantics of $P$.
\fixme{alcc: Why not leave the commented out material in the report?}

% Commented out just to shorten the report.
%To see that this approach works only for finite CSP processes, we consider
%the example where $\Sigma$ is infinite. In this case,
%$\maxrefs(\Stop/\langle\rangle)$ is empty, and so we cannot use this set to
%calculate the refusals of $\Stop$, that is, $\refs(\Stop/\langle\rangle)$ as
%defined above. As with refusals, we also use the transition graph-oriented
%notation $\maxrefs(n) \subseteq r(n)$ to denote the maximal refusals
%associated with graph state $n$: if $n$ is the state reached in the
%transition graph by following the edge labels in trace $s$, then $\maxrefs(n)
%= \maxrefs(P/s)$.

@@

When investigating  tests for failures refinement, the notion of
\emph{acceptances}~\cite{Hennessy:1988:ATP:50497}, which is dual to refusals,
is also useful. An acceptance set of $P/s$ is a subset of its initials
$[P/s]^0$; equivalently, it is a subset of events labelling  outgoing transitions of
$G(P)/s$. If the behaviour of  $P/s$ is deterministic, its only acceptance
equals $[P/s]^0$, because $P/s$ never refuses any of the events contained in
this set. If $P/s$ is nondeterministic, it internally chooses one of its
\emph{minimal acceptance sets} $A$ and never refuses any event in $A$, while
{\it possibly} refusing the events from $[P/s]^0 - A$ and
{\it always} refusing those from $\Sigma - [P/s]^0$.
The acceptances of $P/s$ are denoted by
$\accs(P/s)$, and the minimal acceptances by $\minaccs(P/s)$. They satisfy
the following properties.
%
\begin{eqnarray}
A\in \minaccs(P/s) & \Leftrightarrow & \exists R\in\maxrefs(P/s) \wedge A = \Sigma-R
\label{eq:accref}
\\
\bigcup \{ A~|~A\in \accs(P/s)\} & = & [P/s]^0
\label{eq:accinitials}
\\
 X\in\accs(P/s) &\Leftrightarrow & A\in \minaccs(P/s) \wedge A\subseteq X \subseteq [P/s]^0
 \label{eq:accsubset}
\end{eqnarray}
%
%Note that (\ref{eq:accref}) can be regarded as a definition of minimal
%acceptances by means of maximal refusals. In this case,
%(\ref{eq:accinitials}) and (\ref{eq:accsubset}) are consequences of this
%definition and the fact that refusals are subset-closed. \fixme{alcc: are you
%sure? (4) does not talk about Acc. Is this important?}
%\fixme{jp: I'm sure and I can prove this. However, we don't need this fact, so I suggest to
%removed it.}
%
Exploiting formulas (\ref{eq:accref}), (\ref{eq:accinitials}), and
(\ref{eq:accsubset}), every node of a normalised transition graph can
alternatively be labelled with their minimal acceptances, and this
information is equivalent to that contained in the maximal refusals. Since
process states $P/s$ are equivalently expressed by states $G(P)/s$ of $P$'s
normalised transition graph, we also write $\minaccs(G(P)/s)$ and
note that (\ref{eq:refsAndR}) and (\ref{eq:accref}) imply
\begin{equation}\label{eq:maxrefsminaccs}
\minaccs(G(P)/s) = \{ \Sigma - R | R\in r(G(P)/s) \}.
\end{equation}
\fixme{alcc: proof in the report perhaps?}

@@

Note that the node names including their number suffixes are generated by the
FDR tool. The numbering is generated during the normalisation procedure. So,
the node numbers do not reflect the distance from the initial node Node\_0.
\xbox
\end{example}
%
Summarising, refinement relations between finite-state CSP processes $P, Q$ can be be
expressed by means of their normalised transition graphs
\begin{eqnarray*}
G(P) & = & ( N_P, {\ii n}_P, \Sigma, t_P : N_P\times\Sigma \pfun N_P, r_P : N_P \fun \mathbb{P}\mathbb{P}(\Sigma))
\\
G(Q) & = & ( N_Q, {\ii n}_Q, \Sigma, t_Q : N_Q\times\Sigma \pfun N_Q, r_Q : N_Q \fun \mathbb{P}\mathbb{P}(\Sigma))
\end{eqnarray*}
%
as established by results in the following lemma.
%
\begin{lemma}
  \label{lemma:tgtrcref}
  \begin{eqnarray}
  P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
  \label{eq:trcrefa}
  \\
  \label{eq:failconf}
  P \lessdet_F Q & \Leftrightarrow & P \lessdet_T Q \wedge P\ conf\ Q
  \\
  \label{eq:failrefa}
  P\ conf\ Q & \Leftrightarrow & \nonumber
  \forall s\in\trc(G(Q))\cap \trc(G(P)), R_Q\in r_Q(G(Q)/s):  \nonumber
  \\ & & \tabd
  \exists R_P\in r_P(G(P)/s): R_Q\subseteq R_P
  \\
  \label{eq:failrefb}
   & \Leftrightarrow &
    \forall s\in\trc(G(Q))\cap \trc(G(P)), A_Q\in\minaccs(G(Q)/s):  \nonumber
   \\ & & \tabd
  \exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
 \end{eqnarray}
  \xbox
\end{lemma}
%
The result (\ref{eq:trcrefa}) reflects trace refinement in terms of graph
traces; (\ref{eq:failconf}) expresses failures refinement in terms of traces
refinement and $conf$; (\ref{eq:failrefa}) states how $conf$ can be expressed
by means of the maximal refusal functions of the graphs involved; and
(\ref{eq:failrefb}) states the same in terms of the minimal acceptances that
can be derived from the maximal refusal functions by means of
(\ref{eq:maxrefsminaccs}). \fixme{alcc: I think at least the report should
point to proofs.}

>>>>

In this section, we present CSP and the concept of minimal hitting sets, which
is central to our novel notion of test for failures refinement.

% =========================================================================
\subsection{CSP, Refinement, and Normalised Transition Graphs}

@@

Throughout this paper, the alphabet of the processes, that is the set of
events that are in scope, is denoted by $\Sigma$ and supposed to be finite.
The FDR tool~\cite{fdr} supports model checking and semantic analyses of
finite-state CSP processes.

@@

Two forms of choice support branching behaviour. An external choice $P
\extchoice Q$ between processes $P$ and $Q$ offers to the environment the
initial events of $P$ and $Q$. Once synchronisation takes place, the process
that has offered this event is chosen and the other is discarded. In an
internal choice $P \intchoice Q$, the environment does not have an
opportunity to interfere:~the choice is made by the process.
%
\begin{example}\label{example:CSP}
  We consider $P$, $Q$, and $R$ below. $P$ is initially
  ready to engage in the event $a$, and then makes an internal  choice to
  behave like either $Q$ or $R$.
  \begin{eqnarray*}
  P & = & a \then (Q\intchoice R)
  \\
  Q & = & a \then P \extchoice c \then P
  \\
  R & = & b \then P \extchoice c \then R
  \end{eqnarray*}
  $Q$, for instance, offers to the environment the choice to engage in $a$
  again or $c$. In both cases, afterwards, we have a recursion back to $P$.
  In $R$, if $b$ is chosen, we also have a recursion back to $P$. If $c$ is
  chosen, the recursion is to $R$.
  \xbox
\end{example}
%
Iterated forms $\Extchoice i: I @ P(i)$ and $\Intchoice i: I @ P(i)$ of the
external and internal choice operators allow us to define a choice over a
collection of processes $P(i)$. By convention,  if the index set $I$ is
empty, external choices evaluate to the process $\Stop$, which
deadlocks:~does not engage into any event and does not terminate. An iterated
internal choice is not defined for an empty index set. For an external choice 
indexed over a set of events in the form
$\Extchoice e: A @ e \then P(e), A\subseteq \Sigma$, we use 
abbreviation $e:A \then P(e)$.

@@

Failures refinement, $P \lessdet_F Q$, is defined as expected by set
containment $\fails(Q)\subseteq\fails(P)$. Since refusals are subset-closed,
$P \lessdet_F Q$ implies
$(s,\varnothing)\in\fails(P)$ for all traces $s\in\trc(Q)$. So, for
divergences-free processes, failures refinement implies trace refinement.
Therefore, using the conformance relation
%
\begin{equation}\label{eq:conf}
  Q\ conf\ P \defs \forall s\in \trc(P) \cap \trc(Q): \refs(Q/s)
  \subseteq \refs(P/s),
\end{equation}
%
failures refinement can be expressed by $\lessdet_T$ and $conf$.
%
\begin{equation}\label{thm:fref-tref-conf}
(P \lessdet_F Q) \iff (P \lessdet_T Q \land Q\ conf\ P)
\end{equation}
%

For finite CSP processes, since refusals are
subset-closed, $\refs(P/s)$ can be constructed from the set of \emph{maximal
refusals} defined by
%
\begin{equation}
\maxrefs(P/s) = \{ R \in\refs(P/s)~|~\forall R'\in \refs(P/s) - \{ R\}: R \not\subseteq R'\}
\end{equation}
%
Conversely, with the maximal refusals $\maxrefs(P/s)$ at hand, we can
reconstruct the refusals in the set $\refs(P/s)$ as described by
%
\begin{equation}\label{eq:refMaxRef}
\refs(P/s) = \{ R'\in\power(\Sigma)~|~\exists R\in \maxrefs(P/s): R'\subseteq R \}.
\end{equation}
%
Deterministic process states $P/s$ have exactly the one maximal refusal
defined by $\Sigma-[P/s]^0$, where $[P/s]^0$ denotes the \emph{initials} of
$P/s$, that is, the events that $P/s$ may engage into. The maximal refusals
in combination with the initials of a process express its degree of
nondeterminism.
%
\begin{example}
\label{ex:nondetdegree} $P = (\Stop \intchoice Q)$ has maximal refusals
$\maxrefs(P) = \{ \Sigma \}$, because $\Stop$ refuses to engage in any event,
and this is carried over to $P$ by the internal choice. However, $P$ is
distinguished from $\Stop$ by its initials, which are defined by $[P]^0 = [
\Stop \intchoice Q]^0 = [Q]^0$. So $P$ may engage nondeterministically in any
initial event of $Q$, but also refuse everything, due to internal selection
of $\Stop$.

Assuming an alphabet $\Sigma = \{a,b,c,d\}$, the process
%
$$Q = (e:\{a,b\} \then \Stop) \intchoice (e:\{c,d\} \then \Stop)$$
%
has maximal refusals $\maxrefs(Q) = \{ \{c,d\}, \{a,b\} \}$ and initials
$[Q]^0=\Sigma$. In contrast to $P$, nondeterminism is reflected here by
two maximal refusals. \xbox
\end{example}

@@

The total function $r$ maps each node $n$ to a non-empty set of  (possibly
empty) subsets of $\Sigma$. The graph construction guarantees that
$r(G(P)/s)$ represents the maximal refusals of $P/s$ for all $s\in\trc(P)$.
As a consequence,
\begin{equation}\label{eq:refsAndR}
(s,X)\in\fails(P) \iff s\in\trc(G(P)) \wedge \exists R\in r(G(P)/s): X\subseteq R,
\end{equation}
so $G(P)$ allows us to re-construct the failures semantics of $P$.
%\fixme{alcc: Why not leave the commented out material in the report?}
% Commented out just to shorten the report.
%To see that this approach works only for finite CSP processes, we consider
%the example where $\Sigma$ is infinite. In this case,
%$\maxrefs(\Stop/\langle\rangle)$ is empty, and so we cannot use this set to
%calculate the refusals of $\Stop$, that is, $\refs(\Stop/\langle\rangle)$ as
%defined above. As with refusals, we also use the transition graph-oriented
%notation $\maxrefs(n) \subseteq r(n)$ to denote the maximal refusals
%associated with graph state $n$: if $n$ is the state reached in the
%transition graph by following the edge labels in trace $s$, then $\maxrefs(n)
%= \maxrefs(P/s)$.

@@

When investigating  tests for failures refinement, the notion of
\emph{acceptances}~\cite{Hennessy:1988:ATP:50497}, which is dual to refusals,
is also useful. An acceptance set of $P/s$ is a subset of its initials
$[P/s]^0$; equivalently, it is a subset of events labelling  outgoing transitions of
$G(P)/s$. If the behaviour of  $P/s$ is deterministic, its only acceptance
equals $[P/s]^0$, because $P/s$ never refuses any of the events contained in
this set. If $P/s$ is nondeterministic, it internally chooses one of its
\emph{minimal acceptance sets} $A$ and never refuses any event in $A$, while
{\it possibly} refusing the events from $[P/s]^0 - A$ and
{\it always} refusing those from $\Sigma - [P/s]^0$.
The acceptances of $P/s$ are denoted by
$\accs(P/s)$, and the minimal acceptances by $\minaccs(P/s)$. They satisfy
the following properties.
%
\begin{eqnarray}
A\in \minaccs(P/s) & \Leftrightarrow & \exists R\in\maxrefs(P/s) \wedge A = \Sigma-R
\label{eq:accref}
\\
\bigcup \{ A~|~A\in \accs(P/s)\} & = & [P/s]^0
\label{eq:accinitials}
\\
 X\in\accs(P/s) &\Leftrightarrow & \exists A\in \minaccs(P/s): A\subseteq X \subseteq [P/s]^0
 \label{eq:accsubset}
\end{eqnarray}
%
%Note that (\ref{eq:accref}) can be regarded as a definition of minimal
%acceptances by means of maximal refusals. In this case,
%(\ref{eq:accinitials}) and (\ref{eq:accsubset}) are consequences of this
%definition and the fact that refusals are subset-closed. \fixme{alcc: are you
%sure? (4) does not talk about Acc. Is this important?}
%\fixme{jp: I'm sure and I can prove this. However, we don't need this fact, so I suggest to
%removed it.}
%
Exploiting formula (\ref{eq:accref}), 
%(\ref{eq:accinitials}), and (\ref{eq:accsubset}), 
every node of a normalised transition graph can
alternatively be labelled with their minimal acceptances, and this
information is equivalent to that contained in the maximal refusals. Since
process states $P/s$ are equivalently expressed by states $G(P)/s$ of $P$'s
normalised transition graph, we also write $\minaccs(G(P)/s)$ and
note that (\ref{eq:refsAndR}) and (\ref{eq:accref}) imply
\begin{equation}\label{eq:maxrefsminaccs}
\minaccs(G(P)/s) = \{ \Sigma - R | R\in r(G(P)/s) \}.
\end{equation}
%\fixme{alcc: proof in the report perhaps?}

@@

Note that the node names including their number suffixes are generated by the
FDR tool. The numbering is generated during the normalisation procedure. So,
the node numbers do not reflect the distance from the initial node Node\_0.
\xbox
\end{example}
%
Summarising, refinement relations between finite-state CSP processes $P, Q$ can be be
expressed by means of their normalised transition graphs
\begin{eqnarray*}
G(P) & = & ( N_P, {\ii n}_P, \Sigma, t_P : N_P\times\Sigma \pfun N_P, r_P : N_P \fun \mathbb{P}\mathbb{P}(\Sigma))
\\
G(Q) & = & ( N_Q, {\ii n}_Q, \Sigma, t_Q : N_Q\times\Sigma \pfun N_Q, r_Q : N_Q \fun \mathbb{P}\mathbb{P}(\Sigma))
\end{eqnarray*}
%
as established by the results  in the following lemma.
There, result (\ref{eq:trcrefa}) reflects trace refinement in terms of graph
traces; (\ref{eq:failconf}) expresses failures refinement in terms of traces
refinement and $conf$; (\ref{eq:failrefa}) states how $conf$ can be expressed
by means of the maximal refusal functions of the graphs involved; and
(\ref{eq:failrefb}) states the same in terms of the minimal acceptances that
can be derived from the maximal refusal functions by means of
(\ref{eq:maxrefsminaccs}). 
%%\fixme{alcc: I think at least the report should point to proofs.}
%
\begin{lemma}
  \label{lemma:tgtrcref}
  \begin{eqnarray}
  P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
  \label{eq:trcrefa}
  \\
  \label{eq:failconf}
  P \lessdet_F Q & \Leftrightarrow & P \lessdet_T Q \wedge P\ conf\ Q
  \\
  \label{eq:failrefa}
  Q\ conf\ P & \Leftrightarrow & \nonumber
  \forall s\in\trc(G(Q))\cap \trc(G(P)), R_Q\in r_Q(G(Q)/s):  \nonumber
  \\ & & \tabd
  \exists R_P\in r_P(G(P)/s): R_Q\subseteq R_P
  \\
  \label{eq:failrefb}
   & \Leftrightarrow &
    \forall s\in\trc(G(Q))\cap \trc(G(P)), A_Q\in\minaccs(G(Q)/s):  \nonumber
   \\ & & \tabd
  \exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
 \end{eqnarray}
  \xbox
\end{lemma}
%
\begin{proof}
Recall that $P\lessdet_T Q$ is defined
as $\trc(Q)\subseteq \trc(P)$ and that $\trc(P)=\trc(G(P))$ and $\trc(Q)=\trc(G(Q))$.
This shows (\ref{eq:trcrefa}).

\medskip
\noindent
To prove (\ref{eq:failconf}), we derive
\begin{argue}
P \lessdet_F Q 
\\
\Leftrightarrow \fails(Q)\subseteq \fails(Q) & definition of $\lessdet_F$
\\
\Leftrightarrow \forall (s,X) \in  \fails(Q): (s,X) \in\fails(P) 
& property of $\subseteq$
\\
\Leftrightarrow \forall (s,\varnothing) \in  \fails(Q): (s,\varnothing) \in\fails(P)
\wedge {}
\\\tabc \forall s\in\trc(Q), R\in \refs(Q/s): R\in\refs(P/s)
\\
& Definition of failures, refusals, subset closure
\\
\Leftrightarrow \trc(Q)\subseteq\trc(P)
\wedge {}
\\\tabc \forall s\in\trc(Q), R\in \refs(Q/s): R\in\refs(P/s)
\\
& Definition of failures and traces
\\
\Leftrightarrow \trc(Q)\subseteq\trc(P)
\wedge {}
\\\tabc \forall s\in\trc(Q)\cap\trc(P): \refs(Q/s) \subseteq\refs(P/s)
\\
& Property of $\cap$ and $\subseteq$
\\
\Leftrightarrow
P\lessdet_T Q \wedge Q\ conf\ P
& Definition of $\lessdet_T$ and $conf$
\end{argue}

\medskip
\noindent
To prove (\ref{eq:failrefa}), we derive
\begin{argue}
Q\ conf\ P 
\\
 \Leftrightarrow \forall s\in\trc(P)\cap \trc(Q): \refs(Q/s)\subseteq\refs(P/s)
 \\
 & Definition of $conf$  (\ref{eq:conf})
 \\
 \Leftrightarrow \forall s\in\trc(G(P))\cap \trc(G(Q)): \refs(Q/s)\subseteq\refs(P/s)
 \\
 & $\trc(P) = \trc(G(P))$, $\trc(Q) = \trc(G(Q))$
 \\
\Leftrightarrow \forall s\in\trc(G(P))\cap \trc(G(Q)), R_Q\in r_Q(G(Q)/s):
\\\tabc
\exists R_P\in r_P(G(P)/s): R_Q\subseteq R_P
& Property of $r_P, r_Q$ and (\ref{eq:refMaxRef})
\end{argue}

\medskip
\noindent
Finally, (\ref{eq:failrefb}) follows from (\ref{eq:failrefa}) using (\ref{eq:accref})
and the fact that $R_Q \subseteq R_P$ is equivalent to 
$\Sigma - R_P \subseteq \Sigma - R_Q$.
\xbox
\end{proof}
